---
title: "My Bechdel test"
author: "Rick SCHNEIDER"
date: "1 octobre 2018"
output: html_document
---
https://data.world/sharon/bechdel-test -> new data for bechdel test!!!!!!!


# Packages:
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r,message=FALSE,warning =FALSE}
library(tidyverse)
library(ggplot2)
library(readr)
```


# Introduction

The goal of this new bechdel test is to measure the gender imbalance in movies.

The original Bechdel test tests for 3 criterias:
1)Are there at least 2 women in the movie?
2)Do they have a conversation together?
3)Is that conversation about somthing else than a man?

Fivethirtyeight has created a new Bechdel test.

Import data from the new Benchdel test:
```{r,message=FALSE, warning =FALSE}

new_bechdel <- read_csv("https://raw.githubusercontent.com/fivethirtyeight/data/master/next-bechdel/nextBechdel_allTests.csv")

cast_gender <- read_csv("https://raw.githubusercontent.com/fivethirtyeight/data/master/next-bechdel/nextBechdel_castGender.csv")
crew_gender <- read_csv("https://raw.githubusercontent.com/fivethirtyeight/data/master/next-bechdel/nextBechdel_crewGender.csv")

```
# Analyis of cast_gender & crew_gender

Lets start by having a look the 2 data sets that we have to create our benchdel test:

cast_gender:
```{r}
View(new_bechdel)

head(cast_gender)
dim(cast_gender)
names(cast_gender)
summary(cast_gender)
View(cast_gender)

#How many different movies are in the df?
cast_gender %>% 
  distinct(MOVIE) %>% 
  summarise(count_movies_cast=n())
```
cast_gender is a 2075x6 data frame with the variables "MOVIE" (name of the movie), "ACTOR" (name of the casted actor), "CHARACTER_NAME" (name of the character in the movie), "TYPE" (which role did the character play? Was it a leading, supporting,... one?), "BILLING" (billing numer) and "GENDER" (female or male).
The data frame contains information about 50 different movies.

Lets have a look at crew_gender:
```{r}
head(crew_gender)
dim(crew_gender)
names(crew_gender)
summary(crew_gender)
View(crew_gender)

#How many different movies are in the df?
crew_gender %>% 
  distinct(MOVIE) %>% 
  summarise(count_movies_crew=n())
```
crew_gender is a 10029x7 data frame with the variables "MOVIE", "DEPARTMENT" (in which department did the crew member work?), "FULL_NAME", "FIRST_NAME", "IMDB" (link to the IMDb page of the person in question), "GENDER_PROB" (the probability of the name being female (->0) or male (->1)) and "GENDER_GUESS" (the guess of the gender based on the probability).
crew_gender contais information about 19 different movies. All movie names have the supplement of "(2016)" in their name which can be removed.



#My first Benchdel criteria:
The goal of my personal benchdel test is to test for gender inqueality. Therefore, I am going to introduce a few gender criterias that a movie should fulfill to pass my test. The first criterias that I would like t take into consideration are the following:
1) Over 30% of the cast should be female
2) Leading roles should be 40% female

Next the data set is analysed to see if those criteria are reasonable. In a next step, if necessary, we are going to adapt the criteria

#Analysis of the first Benchdel criteria:
Lets have a look at the feasability of our first criterium, which is: "Over 30% of the cast should be female":
```{r}
#create  count table:
count_gender <- table(cast_gender$GENDER)
count_gender

#create a pie chart to visualize the count:
pie <- ggplot(cast_gender, aes(x = "", fill = factor(GENDER))) + 
  geom_bar(width = 1) +
  theme(axis.line = element_blank(), 
        plot.title = element_text(hjust=0.5)) + 
  labs(fill="GENDER", 
       x=NULL, 
       y=NULL, 
       title="Pie Chart of class", 
       caption="Source: mpg")
  
pie + coord_polar(theta = "y", start=0)

#calculate the percentage ratio:
count_gender <- data.frame(count_gender)
perc_female <- count_gender[count_gender$Var1=="Female",2]/(count_gender[count_gender$Var1=="Female",2]+count_gender[count_gender$Var1=="Male",2])
perc_female*100
```
On average over all movies in our database, around 31.74% of the cast is female. As such, our requirement to have at least 30% females in a cast seems to be a feasible requirement without excluding all the movies.


Lets have a look at the feasability of our first criterium, which is: "Leading roles should be 40% female":

```{r}
#filter out leading characters:
leading_cast <- cast_gender %>%
                  filter(TYPE == "Leading")

#geberate a frequency count table:
leading_gender_count = table(leading_cast$GENDER)
leading_gender_count


#generate a pie chart with the gender of leading people:
pie <- ggplot(leading_cast, aes(x = "", fill = factor(GENDER))) + 
  geom_bar(width = 1) +
  theme(axis.line = element_blank(), 
        plot.title = element_text(hjust=0.5)) + 
  labs(fill="GENDER", 
       x=NULL, 
       y=NULL, 
       title="Pie Chart of class", 
       caption="Source: mpg")
  
pie + coord_polar(theta = "y", start=0)

#calculate the percentage ratio:
leading_gender_count <- data.frame(leading_gender_count)
perc_female <- leading_gender_count[leading_gender_count$Var1=="Female",2]/(leading_gender_count[leading_gender_count$Var1=="Female",2]+leading_gender_count[leading_gender_count$Var1=="Male",2])
perc_female*100

```




# My first Benchdel test:

Criterium 1:
```{r}
#As we need to count the gender for a few criteria, we create a function to have a reproductible code. In R, functions cannot return multiple values, so we need to create 2 seperate functions:
#count females function:
f_count_fem <- function(df){
  num_fem <- df %>% 
                  filter(GENDER == "Female") %>% 
                  group_by(MOVIE) %>% 
                  summarise(count_fem_cast = n())
  return(num_fem)}

#count males function:
f_count_male <- function(df){
  num_male <- df %>% 
                  filter(GENDER == "Male") %>% 
                  group_by(MOVIE) %>% 
                  summarise(count_male_cast = n()) 
  return(num_male)}

num_fem <- f_count_fem(cast_gender)
num_male <- f_count_male(cast_gender)

#Join the count per movie data frames and calculate the ratio:
my_bechdel <- inner_join(num_fem,num_male,by="MOVIE")
my_bechdel <- my_bechdel %>% 
                mutate(crit1_test = count_fem_cast/(count_fem_cast+count_male_cast),
                       crit1 = case_when(       
                          crit1_test > 0.3  ~ 1, crit1_test <= 0.3 ~ 0))      
table(my_bechdel$crit1) 
View(my_bechdel)

```
We see that 31 out of the 50 movies pass this criterium


criterium 2:

```{r}
#use functions to count males and females having a leading role:
num_fem <- f_count_fem(leading_cast)
num_male <- f_count_male(leading_cast)
#View(num_fem)

#Reminder: leading_cast -> information about the leading actors for every movie
#select a list of distinct movies where we have information about a leading actor
my_bechdel2 <- leading_cast %>% 
                  select(MOVIE) %>%  
                   distinct(MOVIE)

#add the female count column:
my_bechdel2 <- right_join(num_fem,my_bechdel2,by="MOVIE")
my_bechdel2[is.na(my_bechdel2[,2]),2]=0
#add a male count column:
my_bechdel2 <- right_join(num_male,my_bechdel2,by="MOVIE")
my_bechdel2[is.na(my_bechdel2[,2]),2]=0

#calculate the ratio:
my_bechdel2 <-  my_bechdel2 %>% 
                    mutate(crit2_test = count_fem_cast/(count_male_cast+count_fem_cast))
#final crit2 (1: passed criterium, 0: not passed)
my_bechdel2 <-  my_bechdel2 %>%
                    mutate(crit1_test = count_fem_cast/(count_fem_cast+count_male_cast),
                       crit2 = case_when(       
                          crit2_test > 0.4  ~ 1, crit2_test <= 0.4 ~ 0)) 
table(my_bechdel2$crit2)
#16 out of 31 movies pass this part of the test (+/- 50%)
            
View(my_bechdel2)

```

Putting the criteria together:
```{r}
rick_test <- my_bechdel
rick_test <- rick_test %>% 
                left_join(my_bechdel2,by="MOVIE") %>% 
                select(MOVIE,crit1,crit2)

#if there is no data available, put a -1
rick_test[is.na(rick_test$crit2),"crit2"]=-1

#how many crit2 are equal to -1?
rick_test %>% 
  filter(crit2 == -1) %>% 
  summarise(count_minus1 = n())
#View(rick_test)
```
#First evaluation:

After implementing the 2 first criteria, we can see that there is a problem for the availability of the data. This means that if we filter for different categories, there might not be data on every movie. For crit2 e.g., there are 19 movies that cannot be tested because of missing data. This can be seen in the following plot: PLOTPLOTPLOT.

We are going to look at the different roles of the of the cast and we are going to check how much data is actually available for the different categories.

```{r}
#this variable stores the amount of data we have in the type column with respect to different movies
tyes_count <- cast_gender %>% 
                  select(MOVIE,TYPE) %>% 
                  group_by(TYPE) %>%
                  distinct(MOVIE) %>% 
                  summarize(count_movies=n()) 

#barplot of our resulting count table:
ggplot(types_count, aes(x=TYPE, y=count_movies)) + 
  geom_bar(stat="identity", width=.5, fill="tomato3") + 
  labs(title="Ordered Bar Chart", 
       subtitle="Make Vs Avg. Mileage", 
       caption="source: mpg") + 
  theme(axis.text.x = element_text(angle=65, vjust=0.6))


```
We can see that the type "leading" provides data on actors with main roles for 31 movies. Only the type "supporting" provides data on every movie. As a result, we should create a criteria based on the proportion of female people with supporting roles in the movies.

We are going to extend the test as follows:
1) Over 30% of the cast should be female
2) Leading roles should be 40% female
3) The supporting actors should be 50% female


We are going to decide in a later step if we are going to reject criterium 2), or if we are going to find a more flexible soluion for this problem.

Lets have a look at the feasability of our third criterium, which is: "The supporting actors should be 50% female":
```{r}

```




We need a solution for this. There are 3 possible scenarios:
1)We do our final test only on the movies where we have all information for our chosen tests
2)we change our criteria in order to test for all the movies
3)we come up with a formula that allows to take missing data into account for the total test (e.g. a movie is eligible for the test if there is enough data on 4 out of the 5 criteria,if 5 --> pass 3 tests and be very close to pass the 4th (we need to introduce a closeness measure!); if 4 --> pass 3 tests )



new test idea--> pass the test if at least 2 female stuntman in a movie


#Additional data

This data set contains the revenues
```{r,message=FALSE, warning =FALSE}
#revenue <- read_csv("data/Bechdel-master_revenue.csv")

#delete the index column and prepare table for join operation:
#revenue <- revenue %>% 
#              select(-1) %>% 
#              rename(MOVIE=Movie)
#View(revenue)

#join the data with a list of movies that we are going to test:
#movie_list <- cast_gender %>% 
#                  select(MOVIE) %>% 
#                  distinct()
#View(movie_list)
#revenue <- inner_join(movie_list,revenue,by="MOVIE")
#View(revenue)

```
Problems: many NAs, not very useful data. Very difficult to join the table based on the name of the movies...


# Ressources

http://bechdeltest.com/

http://poly-graph.co/bechdel/

https://pudding.cool/2017/03/film-dialogue/

https://fivethirtyeight.com/features/the-dollar-and-cents-case-against-hollywoods-exclusion-of-women/

https://fivethirtyeight.com/features/the-workplace-is-even-more-sexist-in-movies-than-in-reality/


